Supplemental tables to figures

### 2025-03-13 manuscript_1_code.Rmd
Added scripts to make supplemental figures

>>>>

# Supplemental tables

Save `emtrends()` output as a table for supplemental figures

## Table S2

For supplemental table S2: cover vs. diversity

```{r}
# get estimates: taxonomic richness
t.s2.a <- as_tibble(emtrends(cover_mod, pairwise ~ habitat, var = "richness")$emtrends) %>% 
  mutate(Predictor = "Taxonomic richness",
         `Spatial scale` = "Plot-level") %>% 
  # rename this so it matches for joining purposes
  rename_if(str_detect(names(.), ".trend"), ~"Mean")

# just want to make sure this^ isn't this (below)?
# emtrends(cover_mod_2, pairwise ~ habitat, var = "richness_mean")

t.s2.b <- as_tibble(emtrends(site_cover_mod, pairwise ~ habitat, var = "richness")$emtrends) %>% 
  mutate(Predictor = "Taxonomic richness",
         `Spatial scale` = "Site-level") %>% 
  rename_if(str_detect(names(.), ".trend"), ~"Mean")

# functional richness
t.s2.c <- as.tibble(emtrends(cover_mod_fg, pairwise ~ habitat, var = "functional_richness")$emtrends) %>% 
  mutate(Predictor = "Functional richness",
         `Spatial scale` = "Plot-level") %>% 
  rename_if(str_detect(names(.), ".trend"), ~"Mean")

# not this right?
# emtrends(cover_mod_fg_2, pairwise ~ habitat, var = "functional_richness_mean")

t.s2.d <- as.tibble(emtrends(site_cover_mod_fg, pairwise ~ habitat, var = "functional_richness")$emtrends) %>% 
  mutate(Predictor = "Functional richness",
         `Spatial scale` = "Site-level") %>% 
  rename_if(str_detect(names(.), ".trend"), ~"Mean")

# not this right?
# emtrends(cover_mod_fg, pairwise ~ habitat, var = "functional_richness")
```

Join:

```{r}
rbind(t.s2.a, t.s2.b, t.s2.c, t.s2.d) %>% 
  mutate(Table = "S2") %>% 
  select(-SE, -df) -> table_s2
```

## Table S3

Stability

```{r}
# get estimates for taxonomic richness
t.s3.a <- as.tibble(emtrends(rich_stab_mod, pairwise ~ habitat, var = "richness_mean")$emtrends) %>% 
  mutate(Predictor = "Taxonomic richness") %>% 
  rename_if(str_detect(names(.), ".trend"), ~"Mean")

# get estimates for fucntional richness
t.s3.b <- as.tibble(emtrends(rich_stab_mod_fg, pairwise ~ habitat, var = "functional_richness_mean")$emtrends) %>% 
  mutate(Predictor = "Functional richness") %>% 
  rename_if(str_detect(names(.), ".trend"), ~"Mean")

# get estimates for synchrony
t.s3.c <- as.tibble(emtrends(synch_stab_mod, pairwise ~ habitat, var = "synchrony")$emtrends) %>% 
  mutate(Predictor = "Synchrony") %>% 
  rename_if(str_detect(names(.), ".trend"), ~"Mean")

Join:

```{r}
rbind(t.s3.a, t.s3.b, t.s3.c) %>% 
  mutate(`Spatial scale` = "Plot-level", 
         Table = "S3") %>% 
  select(-SE, -df) -> table_s3
```

## Table S4

For supplemental table S4: scale figure

```{r}
# get estimates: site-level richness
t.s4.a <- as.tibble(emtrends(rich_stab_mod_site, pairwise ~ habitat, var = "richness_mean")$emtrends) %>% 
  mutate(Predictor = "Site-level taxonomic-richness") %>% 
  rename_if(str_detect(names(.), ".trend"), ~"Mean")

# not this right?
# emtrends(rich_stab_mod, pairwise ~ habitat, var = "richness_mean"

t.s4.b <- as.tibble(emtrends(rich_stab_mod_site_fg, pairwise ~ habitat, var = "functional_richness_mean")$emtrends) %>% 
  mutate(Predictor = "Site-level functional richness") %>% 
  rename_if(str_detect(names(.), ".trend"), ~"Mean")

## CHECK ^^^^^^ -- doesn't match??

t.s4.c <- as.tibble(emtrends(synch_stab_mod_site, pairwise ~ habitat, var = "synchrony")$emtrends) %>% 
  mutate(Predictor = "Site-level species synchrony") %>% 
  rename_if(str_detect(names(.), ".trend"), ~"Mean")

t.s4.d <- as.tibble(emtrends(mean_synchrony_mod, pairwise ~ habitat, var = "synchrony_mean")$emtrends) %>% 
  mutate(Predictor = "Mean plot-level species synchrony") %>% 
  rename_if(str_detect(names(.), ".trend"), ~"Mean")

t.s4.e <- as.tibble(emtrends(alpha_gamma_stab_mod, pairwise ~ habitat, var = "stability_mean")$emtrends) %>% 
  mutate(Predictor = "Plot-level stability") %>% 
  rename_if(str_detect(names(.), ".trend"), ~"Mean")

t.s4.f <- as.tibble(emtrends(spatial_synchrony_mod, pairwise ~ habitat, var = "spatial_synchrony")$emtrends) %>% 
  mutate(Predictor = "Spatial synchrony") %>% 
  rename_if(str_detect(names(.), ".trend"), ~"Mean")
```

Join:

```{r}
rbind(t.s4.a, t.s4.b, t.s4.c,
      t.s4.d, t.s4.e, t.s4.f) %>% 
  mutate(Table = "S4") %>% 
  select(-SE, -df) -> table_s4
```

### Save as a CSV

Join them all together

```{r}
table_s2 %>% 
  full_join(table_s3) %>% 
  full_join(table_s4) %>% 
  # rename to match previous version/code
  rename(Habitat = habitat,
         Lower_CI = asymp.LCL,
         Upper_CI = asymp.UCL) %>%
  # make a blank column to fill in the letter designations manually
  mutate(Letter = NA) %>%
  # save as CSV
  write_csv(here("data/supplemental_tables.csv"))
```

### 2025-03-13 supplemental_table_figures.Rmd
Added scripts to make supplemental figures

```{r}
supp_tables <- read_csv(here("data/supplemental_tables.csv"))
```

@@

```{r}
supp_tables %>% 
  filter(Table == "S2") %>% 
  filter(`Spatial scale` == "Site-level") %>% 
  # order the habitats by distance from shore
  mutate(Habitat = factor(Habitat, levels = c("Forereef 17m", "Forereef 10m",  "Backreef", "Fringing"))) %>% 
  ggplot(aes(x = Mean, y = Habitat, color = Habitat)) +
  geom_point(size = 6) +
  # add confidence intervals:
  geom_linerange(aes(xmin = Lower_CI, xmax = Upper_CI), linewidth = 2.5) +
  facet_wrap(~ Predictor) +
  scale_colour_manual(values = habitat_colours) +
  xlab("Coefficient") +
  ylab("") +
  ggtitle("(b) Site-level") +
  model_themes + 
  # add letters denoting significance
  geom_text(aes(x = Upper_CI + 0.03 , y = Habitat, 
                label = Letter), colour = "black", size = 10) -> s2.site.level
```

@@

```{r}
supp_tables %>% 
  filter(Table == "S4") %>% 
  filter(Predictor == "Site-level taxonomic-richness") %>% 
  # order the habitats by distance from shore
  mutate(Habitat = factor(Habitat, levels = c("Forereef 17m", "Forereef 10m",  "Backreef", "Fringing"))) %>% 
  ggplot(aes(x = Mean, y = Habitat, color = Habitat)) +
  geom_point(size = 6) +
  # add confidence intervals:
  geom_linerange(aes(xmin = Lower_CI, xmax = Upper_CI), linewidth = 2.5) +
  scale_colour_manual(values = habitat_colours) +
  # if you want the 0 reference:
  geom_vline(xintercept = 0, linetype = "dashed", linewidth = 1, color = "gray") +
  xlab("Coefficient") +
  ylab("") +
  ggtitle("(a) Site-level taxonomic-richness") +
  model_themes + 
  # add letters denoting significance
  geom_text(aes(x = Upper_CI + 0.05 , y = Habitat, 
                label = Letter), colour = "black", size = 10) +
  theme(legend.position = "none") -> s4.taxon
```

```{r}
supp_tables %>% 
  filter(Table == "S4") %>% 
  filter(Predictor == "Site-level functional-richness") %>% 
  # order the habitats by distance from shore
  mutate(Habitat = factor(Habitat, levels = c("Forereef 17m", "Forereef 10m",  "Backreef", "Fringing"))) %>% 
  ggplot(aes(x = Mean, y = Habitat, color = Habitat)) +
  geom_point(size = 6) +
  # add confidence intervals:
  geom_linerange(aes(xmin = Lower_CI, xmax = Upper_CI), linewidth = 2.5) +
  scale_colour_manual(values = habitat_colours) +
    # if you want the 0 reference:
  geom_vline(xintercept = 0, linetype = "dashed", linewidth = 1, color = "gray") +
  xlab("Coefficient") +
  ylab("") +
  ggtitle("(b) Site-level functional-richness") +
  model_themes + 
  # add letters denoting significance
  geom_text(aes(x = Upper_CI + 0.1 , y = Habitat, 
                label = Letter), colour = "black", size = 10) +
  theme(legend.position = "none") -> s4.functional
```

@@

@@

```{r}
supp_tables %>% 
  filter(Table == "S4") %>% 
  filter(Predictor == "Spatial synchrony") %>% 
  # order the habitats by distance from shore
  mutate(Habitat = factor(Habitat, levels = c("Forereef 17m", "Forereef 10m",  "Backreef", "Fringing"))) %>% 
  ggplot(aes(x = Mean, y = Habitat, color = Habitat)) +
  geom_point(size = 6) +
  # add confidence intervals:
  geom_linerange(aes(xmin = Lower_CI, xmax = Upper_CI), linewidth = 2.5) +
  scale_colour_manual(values = habitat_colours) +
    # if you want the 0 reference:
  geom_vline(xintercept = 0, linetype = "dashed", linewidth = 1, color = "gray") +
  xlab("Coefficient") +
  ylab("") +
  ggtitle("(f) Spatial synchrony") +
  model_themes + 
  # add letters denoting significance
  geom_text(aes(x = Upper_CI + 0.4 , y = Habitat, 
                label = Letter), colour = "black", size = 10) +
  theme(legend.position = "none") -> s4.plt.synch
```

>>>>

```{r}
supp_tables <- read_csv(here("data/supplemental_tables_manual_letters.csv"))
```

@@

```{r}
supp_tables %>% 
  filter(Table == "S2") %>% 
  filter(`Spatial scale` == "Site-level") %>% 
  # order the habitats by distance from shore
  mutate(Habitat = factor(Habitat, levels = c("Forereef 17m", "Forereef 10m",  "Backreef", "Fringing"))) %>% 
  ggplot(aes(x = Mean, y = Habitat, color = Habitat)) +
  geom_point(size = 6) +
  # add confidence intervals:
  geom_linerange(aes(xmin = Lower_CI, xmax = Upper_CI), linewidth = 2.5) +
  facet_wrap(~ Predictor) +
  scale_colour_manual(values = habitat_colours) +
  xlab("Coefficient") +
  ylab("") +
  ggtitle("(b) Site-level") +
  # if you want the 0 reference:
  geom_vline(xintercept = 0, linetype = "dashed", linewidth = 1, color = "gray") +
  model_themes + 
  # add letters denoting significance
  geom_text(aes(x = Upper_CI + 0.03 , y = Habitat, 
                label = Letter), colour = "black", size = 10) -> s2.site.level
```

@@

```{r}
supp_tables %>% 
  filter(Table == "S4") %>% 
  filter(Predictor == "Site-level taxonomic-richness") %>% 
  # order the habitats by distance from shore
  mutate(Habitat = factor(Habitat, levels = c("Forereef 17m", "Forereef 10m",  "Backreef", "Fringing"))) %>% 
  ggplot(aes(x = Mean, y = Habitat, color = Habitat)) +
  geom_point(size = 6) +
  # add confidence intervals:
  geom_linerange(aes(xmin = Lower_CI, xmax = Upper_CI), linewidth = 2.5) +
  scale_colour_manual(values = habitat_colours) +
  # if you want the 0 reference:
  geom_vline(xintercept = 0, linetype = "dashed", linewidth = 1, color = "gray") +
  xlab("Coefficient") +
  ylab("") +
  ggtitle("(a) Site-level taxonomic richness") +
  model_themes + 
  # add letters denoting significance
  geom_text(aes(x = Upper_CI + 0.05 , y = Habitat, 
                label = Letter), colour = "black", size = 10) +
  theme(legend.position = "none") -> s4.taxon
```

```{r}
supp_tables %>% 
  filter(Table == "S4") %>% 
  filter(Predictor == "Site-level functional richness") %>% 
  # order the habitats by distance from shore
  mutate(Habitat = factor(Habitat, levels = c("Forereef 17m", "Forereef 10m",  "Backreef", "Fringing"))) %>% 
  ggplot(aes(x = Mean, y = Habitat, color = Habitat)) +
  geom_point(size = 6) +
  # add confidence intervals:
  geom_linerange(aes(xmin = Lower_CI, xmax = Upper_CI), linewidth = 2.5) +
  scale_colour_manual(values = habitat_colours) +
    # if you want the 0 reference:
  geom_vline(xintercept = 0, linetype = "dashed", linewidth = 1, color = "gray") +
  xlab("Coefficient") +
  ylab("") +
  ggtitle("(b) Site-level functional richness") +
  model_themes + 
  # add letters denoting significance
  geom_text(aes(x = Upper_CI + 0.1 , y = Habitat, 
                label = Letter), colour = "black", size = 10) +
  theme(legend.position = "none") -> s4.functional
```

@@

Plot-level stability

```{r}
supp_tables %>% 
  filter(Table == "S4") %>% 
  filter(Predictor == "Plot-level stability") %>% 
  # order the habitats by distance from shore
  mutate(Habitat = factor(Habitat, levels = c("Forereef 17m", "Forereef 10m",  "Backreef", "Fringing"))) %>% 
  ggplot(aes(x = Mean, y = Habitat, color = Habitat)) +
  geom_point(size = 6) +
  # add confidence intervals:
  geom_linerange(aes(xmin = Lower_CI, xmax = Upper_CI), linewidth = 2.5) +
  scale_colour_manual(values = habitat_colours) +
  # if you want the 0 reference:
  geom_vline(xintercept = 0, linetype = "dashed", linewidth = 1, color = "gray") +
  xlab("Coefficient") +
  ylab("") +
  ggtitle("(e) Plot-level stability") +
  model_themes + 
  # add letters denoting significance
  geom_text(aes(x = Upper_CI + 0.1 , y = Habitat, 
                label = Letter), colour = "black", size = 10) -> s4.plt.stab
```

@@

```{r}
supp_tables %>% 
  filter(Table == "S4") %>% 
  filter(Predictor == "Spatial synchrony") %>% 
  # order the habitats by distance from shore
  mutate(Habitat = factor(Habitat, levels = c("Forereef 17m", "Forereef 10m",  "Backreef", "Fringing"))) %>% 
  ggplot(aes(x = Mean, y = Habitat, color = Habitat)) +
  geom_point(size = 6) +
  # add confidence intervals:
  geom_linerange(aes(xmin = Lower_CI, xmax = Upper_CI), linewidth = 2.5) +
  scale_colour_manual(values = habitat_colours) +
    # if you want the 0 reference:
  geom_vline(xintercept = 0, linetype = "dashed", linewidth = 1, color = "gray") +
  xlab("Coefficient") +
  ylab("") +
  ggtitle("(f) Spatial synchrony") +
  model_themes + 
  # add letters denoting significance
  geom_text(aes(x = Upper_CI + 0.4 , y = Habitat, 
                label = Letter), colour = "black", size = 10) +
  theme(legend.position = "none") -> s4.spat.synch
```
